More Tests

### 2022-09-18 Manuscript/Block-Bootstrap.Rmd
Set Random Seed

@@

print(root_0.2_1)
```
```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(225, 0.2, 0.1, 15, m1)))
root_0.2_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_2 <- cbind(root_0.2_2, c(n, l, t))
}

print(root_0.2_2)
```
Observed coverage rates seem to be lower...

@@

print(root_0.4_2)
```
Coverage for n = 256 below .90.

@@

print(root_0.6_1)
```

@@

print(root_0.6_2)
```

@@

Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the moving methods.

@@

print(root_0.6_4)
```
9 out of the 10 coverage rates are below .90.

@@

print(root_0.8_1)
```

@@

print(root_0.8_2)
```

@@

print(root_0.8_3)
```
Observed coverage rates seem to be lower, when n was 841 and 784, coverage rates below .90 were recorded for non-moving method, and when n was 900, coverage rate fro moving method was below .90.

@@

>>>>

```{r}
set.seed(5)
```

@@

print(root_0.2_1)
```

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(225, 0.2, 0.1, 15, m1)))
root_0.2_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_2 <- cbind(root_0.2_2, c(n, l, t))
}

print(root_0.2_2)
```
Observed coverage rates seem to be lower, all are lower than .92 for n <= 225.

@@

print(root_0.4_2)
```
All coverage rates below .92 for n <= 441. Coverage for n = 256 below .90 for both methods.

@@

print(root_0.6_1)
```
Coverage rates seem pretty good at this range of n values.

@@

print(root_0.6_2)
```
Coverage rates are still pretty good.

@@

Observed coverage rates seem to be lower, when n was 324, a coverage rate below .90 was recorded for the moving method. When n was 256, both coverage rates were below .90. All coverage rates are below .92.

@@

print(root_0.6_4)
```
8 out of the 10 coverage rates are below .90.

@@

print(root_0.8_1)
```
Coverage rates generally seem good at this range.

@@

print(root_0.8_2)
```
Coverage rates still seem pretty good.

@@

print(root_0.8_3)
```
Observed coverage rates seem to be lower, when n was 841 and 784, coverage rates below .90 were recorded for non-moving method, and when n was 900, coverage rate for moving method was below .90. All coverage rates below .92.

@@

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 10, m1)))
constant_0.2_1 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_1 <- cbind(constant_0.2_1, c(n, 10, t))

print(constant_0.2_1)
```
Coverage rates are good.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(300, 0.2, 0.1, 10, m1)))
constant_0.2_2 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_2 <- cbind(constant_0.2_2, c(n, 10, t))

print(constant_0.2_2)
```
Coverage rates are still good.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(200, 0.2, 0.1, 10, m1)))
constant_0.2_3 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_3 <- cbind(constant_0.2_3, c(n, 10, t))

print(constant_0.2_3)
```
For n <= 180, coverage rates are below .92. For n = 140, both coverage rates are below .90, and the moving method has a coverage rate below .90 for n = 120.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
constant_0.2_4 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_4 <- cbind(constant_0.2_4, c(n, 10, t))

print(constant_0.2_4)
```
Coverage rates are poor.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(600, 0.4, 0.1, 10, m1)))
constant_0.4_1 <- data.frame(c(600, 10, o))
for(m in 29:26)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_1 <- cbind(constant_0.4_1, c(n, 10, t))

print(constant_0.4_1)
```
Good coverage rates.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(500, 0.4, 0.1, 10, m1)))
constant_0.4_2 <- data.frame(c(500, 10, o))
for(m in 24:21)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_2 <- cbind(constant_0.4_2, c(n, 10, t))

print(constant_0.4_2)
```

Good coverage rates.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 10, m1)))
constant_0.4_3 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_3 <- cbind(constant_0.4_3, c(n, 10, t))

print(constant_0.4_3)
```

Still good.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(300, 0.4, 0.1, 10, m1)))
constant_0.4_4 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_4 <- cbind(constant_0.4_4, c(n, 10, t))

print(constant_0.4_4)
```

Coverage rates still pretty good.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(200, 0.4, 0.1, 10, m1)))
constant_0.4_5 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_5 <- cbind(constant_0.4_5, c(n, 10, t))

print(constant_0.4_5)
```

Non-moving method resulted in coverage rate below .90 for n = 200. All coverage rates for n = 140 and 120 are below .90.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
constant_0.4_6 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_6 <- cbind(constant_0.4_6, c(n, 10, t))

print(constant_0.4_6)
```

Poor coverage rates.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 10, m1)))
constant_0.6_1 <- data.frame(c(900, 10, o))
for(m in 44:41)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_1 <- cbind(constant_0.6_1, c(n, 10, t))

print(constant_0.6_1)
```

All coverage rates below .92.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(800, 0.6, 0.1, 10, m1)))
constant_0.6_2 <- data.frame(c(800, 10, o))
for(m in 39:36)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_2 <- cbind(constant_0.6_2, c(n, 10, t))

print(constant_0.6_2)
```

Moving coverage rate for n = 760 is below .90.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(700, 0.6, 0.1, 10, m1)))
constant_0.6_3 <- data.frame(c(700, 10, o))
for(m in 34:31)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_3 <- cbind(constant_0.6_3, c(n, 10, t))

print(constant_0.6_3)
```
All coverage rates below .92 except those for n = 680.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(600, 0.6, 0.1, 10, m1)))
constant_0.6_4 <- data.frame(c(600, 10, o))
for(m in 29:26)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_4 <- cbind(constant_0.6_4, c(n, 10, t))

print(constant_0.6_4)
```

All coverage rates below .92 except those for n = 540.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(500, 0.6, 0.1, 10, m1)))
constant_0.6_5 <- data.frame(c(500, 10, o))
for(m in 24:21)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_5 <- cbind(constant_0.6_5, c(n, 10, t))

print(constant_0.6_5)
```

Coverage rates are generally good.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 10, m1)))
constant_0.6_6 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_6 <- cbind(constant_0.6_6, c(n, 10, t))

print(constant_0.6_6)
```

All coverage rates below .92 for n <= 380. Coverage rates below .90 for n = 360 and 340.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(300, 0.6, 0.1, 10, m1)))
constant_0.6_7 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_7 <- cbind(constant_0.6_7, c(n, 10, t))

print(constant_0.6_7)
```
```{r} 
colnames(root_0.2_1) <- NULL
colnames(root_0.2_2) <- NULL
colnames(root_0.2_3) <- NULL
root_0.2_3
```

```{r}

root_0.2 <- data.frame(rbind(t(root_0.2_1[c(1, 2, 7),]), t(root_0.2_1[c(1, 2, 11),]), t(root_0.2_2[c(1, 2, 7),]), t(root_0.2_2[c(1, 2, 11),]), t(root_0.2_3[c(1, 2, 7),]), t(root_0.2_3[c(1, 2, 11),])))
rownames(root_0.2) <- NULL
colnames(root_0.2) <- c("n", "l", 'ci')
root_0.2['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
root_0.2
```
```{r}
library(ggplot2)
ggplot(root_0.2, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('root_0.2.pdf')
```
```{r}
root_0.4 <- data.frame(rbind(t(root_0.4_1[c(1, 2, 7),]), t(root_0.4_1[c(1, 2, 11),]), t(root_0.4_2[c(1, 2, 7),]), t(root_0.4_2[c(1, 2, 11),]), t(root_0.4_3[c(1, 2, 7),]), t(root_0.4_3[c(1, 2, 11),]), t(root_0.4_4[c(1, 2, 7),]), t(root_0.4_4[c(1, 2, 11),])))
rownames(root_0.4) <- NULL
colnames(root_0.4) <- c("n", "l", 'ci')
root_0.4['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
root_0.4
```
```{r}
library(ggplot2)
ggplot(root_0.4, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('root_0.4.pdf')
```
```{r}
root_0.6 <- data.frame(rbind(t(root_0.6_1[c(1, 2, 7),]), t(root_0.6_1[c(1, 2, 11),]), t(root_0.6_2[c(1, 2, 7),]), t(root_0.6_2[c(1, 2, 11),]), t(root_0.6_3[c(1, 2, 7),]), t(root_0.6_3[c(1, 2, 11),]), t(root_0.6_4[c(1, 2, 7),]), t(root_0.6_4[c(1, 2, 11),])))
rownames(root_0.6) <- NULL
colnames(root_0.6) <- c("n", "l", 'ci')
root_0.6['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
root_0.6
```

```{r}
library(ggplot2)
ggplot(root_0.6, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('root_0.6.pdf') 
```
```{r}
root_0.8 <- data.frame(rbind(t(root_0.8_1[c(1, 2, 7),]), t(root_0.8_1[c(1, 2, 11),]), t(root_0.8_2[c(1, 2, 7),]), t(root_0.8_2[c(1, 2, 11),]), t(root_0.8_3[c(1, 2, 7),]), t(root_0.8_3[c(1, 2, 11),]), t(root_0.8_4[c(1, 2, 7),]), t(root_0.8_4[c(1, 2, 11),])))
rownames(root_0.8) <- NULL
colnames(root_0.8) <- c("n", "l", 'ci')
root_0.8['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
root_0.8
```

```{r}
library(ggplot2)
ggplot(root_0.8, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('root_0.8.pdf') 
```
```{r}
constant_0.2 <- data.frame(rbind(t(constant_0.2_1[c(1, 2, 7),]), t(constant_0.2_1[c(1, 2, 11),]), t(constant_0.2_2[c(1, 2, 7),]), t(constant_0.2_2[c(1, 2, 11),]), t(constant_0.2_3[c(1, 2, 7),]), t(constant_0.2_3[c(1, 2, 11),]), t(constant_0.2_4[c(1, 2, 7),]), t(constant_0.2_4[c(1, 2, 11),])))
rownames(constant_0.2) <- NULL
colnames(constant_0.2) <- c("n", "l", 'ci')
constant_0.2['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
constant_0.2
```

```{r}
library(ggplot2)
ggplot(constant_0.2, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('constant_0.2.pdf')  
```
```{r}
constant_0.4 <- data.frame(rbind(t(constant_0.4_1[c(1, 2, 7),]), t(constant_0.4_1[c(1, 2, 11),]), t(constant_0.4_2[c(1, 2, 7),]), t(constant_0.4_2[c(1, 2, 11),]), t(constant_0.4_3[c(1, 2, 7),]), t(constant_0.4_3[c(1, 2, 11),]), t(constant_0.4_4[c(1, 2, 7),]), t(constant_0.4_4[c(1, 2, 11),]), t(constant_0.4_5[c(1, 2, 7),]), t(constant_0.4_5[c(1, 2, 11),]), t(constant_0.4_6[c(1, 2, 7),]), t(constant_0.4_6[c(1, 2, 11),])))
rownames(constant_0.4) <- NULL
colnames(constant_0.4) <- c("n", "l", 'ci')
constant_0.4['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
constant_0.4
```

```{r}
library(ggplot2)
ggplot(constant_0.4, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('constant_0.4.pdf')  
```
```{r}
constant_0.6 <- data.frame(rbind(t(constant_0.6_1[c(1, 2, 7),]), t(constant_0.6_1[c(1, 2, 11),]), t(constant_0.6_2[c(1, 2, 7),]), t(constant_0.6_2[c(1, 2, 11),]), t(constant_0.6_3[c(1, 2, 7),]), t(constant_0.6_3[c(1, 2, 11),]), t(constant_0.6_4[c(1, 2, 7),]), t(constant_0.6_4[c(1, 2, 11),]), t(constant_0.6_5[c(1, 2, 7),]), t(constant_0.6_5[c(1, 2, 11),]), t(constant_0.6_6[c(1, 2, 7),]), t(constant_0.6_6[c(1, 2, 11),]), t(constant_0.6_7[c(1, 2, 7),]), t(constant_0.6_7[c(1, 2, 11),])))
rownames(constant_0.6) <- NULL
colnames(constant_0.6) <- c("n", "l", 'ci')
constant_0.6['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
constant_0.6
```

```{r}
library(ggplot2)
ggplot(constant_0.6, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('constant_0.6.pdf')  
```

```{r}
constant_0.8 <- data.frame(rbind(t(constant_0.8_1[c(1, 2, 7),]), t(constant_0.8_1[c(1, 2, 11),])))
rownames(constant_0.8) <- NULL
colnames(constant_0.8) <- c("n", "l", 'ci')
constant_0.8['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
constant_0.8
```

```{r}
library(ggplot2)
ggplot(constant_0.8, aes(x = n, y = ci, color = method)) +
  geom_line() +
  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
ggsave('constant_0.8.pdf')  
```
